Point-process based representation learning for Electronic Health Records

### 2023-03-10 Manuscript_v1.tex
update
Updates from Overleaf

[imputation methods] Imputation techniques are widely used in electronic health records (EHRs) to handle missing data. Imputation refers to the process of filling in the missing data with plausible values based on the available information. There are several imputation techniques available, each with its strengths and weaknesses. For example, mean imputation replaces missing values with the mean of the available values in the same column, while regression imputation uses a regression model to estimate the missing values based on the relationship between the variables. Other popular imputation methods include multiple imputations, hot deck imputation, and k-nearest neighbors imputation. The choice of imputation technique depends on the type and amount of missing data, as well as the goals of the analysis. Regardless of the technique used, it is important to carefully consider the impact of imputed values on the analysis and to report the imputation method used in the results.

@@

We argue that event encoding could lead to better representation learning in EHRs although it does not necessarily leads to better performance. Patient representation that can respect the irregular sampling pattern in EHRs could have various applications in synthetic data generation.

>>>>

[imputation methods] Imputation techniques are widely used in electronic health records (EHRs) to handle missing data. Imputation refers to the process of filling in the missing data with plausible values based on the available information. There are several imputation techniques available, each with its strengths and weaknesses. For example, mean imputation replaces missing values with the mean of the available values in the same column, while regression imputation uses a regression model to estimate the missing values based on the relationship between the variables. Other popular imputation methods include multiple imputations, hot deck imputation, and k-nearest neighbors imputation. The choice of imputation technique depends on the type and amount of missing data, as well as the goals of the analysis. Regardless of the technique used, it is important to carefully consider the impact of imputed values on the analysis and to report the imputation method used in the results.https://www.overleaf.com/project/63c00678bca7836b32514494

@@

We argue that event encoding could lead to better representation learning in EHRs although it does not necessarily leads to better performance. Patient representation that can respect the irregular sampling pattern in EHRs could have various applications in synthetic data generation..
